### 2019-11-27 paper/paper.tex
Typo fixes from Overleaf

In $N (k \mathbin{:} 1) \mathbin{:} M$ scheduling, we have $N$ units of work mapped onto $M$ CPU threads. Additionally, each of those units of work may be composed of $k$ cooperatively scheduled tasks. This is achieved by pinning the $k$ tasks in a group to one CPU thread, while load balancing units of work across the available cores using the \verb|partr| scheduler, a novel implementation of a parallel depth-first scheduling algorithm. This will discussed future in section \ref{subsub:implementation}.

@@

The algorithm given here is limited in the theoretical scaling capability, since the merge step is not parallelized. On large core counts, that can be important, so please see our supplementary code in \ref{subsub:pmerge}.

@@

For doing the merge step of a merge sort in parallel, we only need to add a bit of code to the \verb|merge!| function. Let's call the result \verb|`merge!|. The details of this algorithm can be found elsewhere, although most textbooks do not give the stable algorithm used here. This is a minor enhancement and simplification of the algorithm given in the original paper\cite{Gavril:1975:MPP:361020.361216}, as described in ``Structured Parallel Programming"\cite{McCool:2012:SPP:2385466} in section 13.1 on page 300, and in a later \href{https://software.intel.com/en-us/articles/a-parallel-stable-sort-using-c11-for-tbb-cilk-plus-and-openmp}{blog post by one of the authors}\cite{parallel-merge-intel}.

>>>>

In $N (k \mathbin{:} 1) \mathbin{:} M$ scheduling, we have $N$ units of work mapped onto $M$ CPU threads. Additionally, each of those units of work may be composed of $k$ cooperatively scheduled tasks. This is achieved by pinning the $k$ tasks in a group to one CPU thread, while load balancing units of work across the available cores using the \verb|partr| scheduler, a novel implementation of a parallel depth-first scheduling algorithm. This will be discussed further in section \ref{subsub:implementation} on implementation.

@@

The algorithm given here is limited in the theoretical scaling capability, since the merge step is not parallelized. On large core counts, that can be important, so please see our supplementary code in appendix \ref{subsub:pmerge} for the version with optimal theoretical scaling.

@@

For doing the merge step of a merge sort in parallel, we only need to add a bit of code to the \verb|merge!| function. Let's call the result \verb|merge!|. The details of this algorithm can be found elsewhere, although most textbooks do not give the stable algorithm used here. This is a minor enhancement and simplification of the algorithm given in the original paper\cite{Gavril:1975:MPP:361020.361216}, as described in ``Structured Parallel Programming''\cite{McCool:2012:SPP:2385466} in section 13.1 on page 300, and in a later \href{https://software.intel.com/en-us/articles/a-parallel-stable-sort-using-c11-for-tbb-cilk-plus-and-openmp}{blog post by one of the authors}\cite{parallel-merge-intel}.
